Approximation as Differentiation

### 2025-05-08 main/formal-structures.tex
Reindexing.
Yes prefer this version of families because reindexing is nicer.

This pattern of objects and morphisms is exactly the \emph{Grothendieck construction} for a particular indexed
category $T: \Set^\op \to \Cat$, namely the functor which assigns to every set $X$ the functor category $T(X)
= \Func{X}{\LatGal}$. Here the (discrete) category $X$ is a plain set and so $\Func{X}{\LatGal}$ is exactly
the category of $X$-indexed families of bounded lattices, with $X$-indexed families of Galois connections
between them as morphisms. The Grothendieck construction $\Grothendieck{}T$ is the ``total category'' which
gloms all such $\Set$-indexed families of bounded lattices into the same category, with reindexing morphisms
to transport between different indexing sets.

\begin{definition}[Functor category of $X$-indexed families]
\label{def:fam:Fam}
For any set $X$ (interpreted as a discrete category) and any category $\cat{C}$, recall that the functor
category $\Func{X}{C}$ has as objects all functors $F: X \to \cat{C}$, namely $X$-indexed families of objects
of $\cat{C}$, and as morphisms from $F \to G$, all families of morphisms $\eta(x): F(x) \to G(x)$ in $\cat{C}$
for every $x \in X$, with naturality trivial because $X$ only has identity morphisms.
\end{definition}

>>>>

This pattern of objects and morphisms is exactly the \emph{Grothendieck construction} for a particular indexed
category $T: \Set^\op \to \Cat$, namely the functor which assigns to every set $X$ the functor category $T(X)
= \Func{X}{\LatGal}$. Here the (discrete) category $X$ is a plain set and so $\Func{X}{\LatGal}$ is exactly
the category of $X$-indexed families of bounded lattices, with $X$-indexed families of Galois connections
between them as morphisms. The Grothendieck construction $\Grothendieck{}T$ is the ``total category'' which
gloms all such $\Set$-indexed families of bounded lattices into the same category, with reindexing morphisms
transporting between data indexed by different sets.

\begin{definition}[Functor category of $X$-indexed families]
\label{def:fam:Fam}
For any set $X$ (interpreted as a discrete category) and any category $\cat{C}$, recall that the functor
category $\Func{X}{\cat{C}}$ has as objects all functors $F: X \to \cat{C}$, namely $X$-indexed families of
objects of $\cat{C}$, and as morphisms from $F \to G$, all families of morphisms $\eta(x): F(x) \to G(x)$ in
$\cat{C}$ for every $x \in X$, with naturality trivial because $X$ only has identity morphisms.
\end{definition}

Like any functor category $\Func{X}{\cat{C}}$ inherits limits and colimits from its codomain.

\begin{proposition}
If $\cat{C}$ has limits (resp.~colimits) then $\Func{X}{\cat{C}}$ has limits (resp.~colimits) computed
pointwise.
\end{proposition}

\begin{definition}[Reindexing]
For any function $f: X \to Y$ define the \emph{reindexing} functor $\reindex{-}{f}: \Func{Y}{\cat{C}} \to
\Func{X}{\cat{C}}$ which sends any $Y$-indexed family $F$ over $\cat{C}$ to the $X$-indexed family
$\reindex{F}{f} = F \comp f$, with $f$ interpreted as the unique functor between $X$ and $Y$ as discrete
categories.
\end{definition}

\begin{definition}
Let $\Func{-}{\cat{C}}: \Set^{\op} \to \Cat$ denote the indexed category which sends any set $X$ to the
category $\Func{X}{\cat{C}}$ and any function $f: X \to Y$ to the functor $\reindex{-}{f}: \Func{Y}{\cat{C}}
\to \Func{X}{\cat{C}}$.
\end{definition}
